### 2016-12-08 discussion.tex
report with tentative section headers and todo list

@@

\section{Macroscopic Perspective of Traffic Interaction}
For this section of the problem, we will model the behaviors of cars in a stream of traffic individually. We will then simulate the movement of this stream of cars and demonstrate some well known traffic phenomenon (cars starting from a red traffic light will propagate forward in a wave formation, cars traveling along a straight road will oscillate into a traffic jam). Furthermore, we will use different controllers to simulate the means by which cars can control their acceleration and will be able to simulate the effect that autonomous cars may have for the throughput of a stream of traffic for varying car densities. This numerical analysis can be contrasted to the analytical solution that was presented in (**another section 2?**).\par
A cars speed is governed by the laws of motion:
\begin{equation}
v_f = v_i + a\Delta t
\end{equation}

An individual car can be modeled as such over a 100,000m track and asked to travel at $v_{target} = 60miles.h^{-1}$ (i.e. $26.8m.s^{-1}$). As, the driver is not an perfect controller he is unable to hold the speed exactly at $v_{target}$. We can therefore model his fluctuations as random acceleration with the corresponding adjustments to correct the acceleration:
\begin{equation}
a_{correction_i} = \alpha(v_{instant} - v_{target}) + N(0,\sigma_1)
\end{equation}

@@

>>>>

\section{Macroscopic Perspective of Traffic Interaction}
There are generally two ways to model traffic. In the macroscopic perspective, traffic is viewed as a fluid or gas with a given maximum density moving according to the laws of conservation of mass. Because we'd like to interweave different models for specific cars, these models would be difficult to blend in a way that is easily interpretable.

@@

\section{Microscopic Perspective of Traffic Interaction : \\Intelligent Driver Models}
In the microscopic perspective, individual cars are modeled as particles that move according to a relationship to their leading particle(s).
For this section of the problem, we will model the behaviors of cars in a stream of traffic individually. We will then simulate the movement of this stream of cars and demonstrate some well known traffic phenomenon (cars starting from a red traffic light will propagate forward in a wave formation, cars traveling along a straight road will oscillate into a traffic jam). Furthermore, we will use different controllers to simulate the means by which cars can control their acceleration and will be able to simulate the effect that autonomous cars may have for the throughput of a stream of traffic for varying car densities. This numerical analysis can be contrasted to the analytical solution that was presented in (**another section 2?**).\par
A car`s speed is governed by the laws of motion:
\begin{equation}
v_f = v_i + a\Delta t
\end{equation}

An individual car can be modeled as such over a 100,000m track and asked to travel at $v_{target} = 60miles.h^{-1}$ (i.e. $26.8m.s^{-1}$). As the driver is not an perfect controller he is unable to hold the speed exactly at $v_{target}$. We can therefore model his fluctuations as random acceleration with the corresponding adjustments to correct the acceleration:
\begin{equation}
a_{correction_i} = \alpha(v_{instant} - v_{target}) + N(0,\sigma_1)
\end{equation}

@@

\section{Microscopic Perspective of Traffic Interaction : Human Driver Models}

\section{Numerical Simulations of Traffic Systems}

\section{Stability Comparison of a Variety of Numerical Integration Schemes}

\section{String Stability of Traffic Systems to Perturbation}

\section{Optimization of Traffic Systems}

\section{TODO}
run stability analysis of Runge Kutta schemes \\
develop a way to run smaller timesteps over any portion we think is likely to explode (although not actually sure how much this will help) \\
develop a cost function for emissions/energy usage and optimize over that \\
can we find the parameters that will cause a phantom traffic jam?
